---
title: "Analysis on Japan&United State"
author:
- familyname: Wang
  othernames: Shu
  address: Monash Universtidy
  email: swan0249@student.monash.edu
  correspondingauthor: true
  qualifications:  Student
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false

---


```{r echo=FALSE, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(fig.path = "Figures/", fig.align ="center",
                      out.width = "50%",
                      messages = FALSE, 
                      warning = FALSE)

# Loading Libraries
library(tidyverse)
library(readr)
library(kableExtra)
library(tinytex)
library(bookdown)
library(naniar)
library(visdat)
library(citation)
library(knitr)
library(scales)
library(patchwork)
```



\newpage
\section*{Country United State and Japan"}
\addcontentsline{toc}{subsection}{Introduction}
\subsection*{Introduction}
With the improvement of people's living standards, more and more people begin to pay attention to diet. As we all know, a healthy diet can help us maintain a healthy body and figure, and effectively prevent dangerous diseases such as high blood pressure and high blood lipids. In our daily diet, our calorie intake mainly comes from three major nutrients, namely protein, fat and carbohydrates. Studies have shown that the proportion of the three major nutrients in the daily diet plays a very important role in human health. On the other hand, people in different regions have different eating habits due to differences in climate and terrain. The food culture of each country is very different, Americans love sweets and bread, Japanese love seafood and small dishes.
In this report, I study the differences in diet between the United States and Japan and analyze the changes in the per capita calorie intake and the intake of the three major nutrients in the United States and Japan since 1960, starting from two aspects of eating habits and time trends A comparative analysis of the eating habits and health of the two countries.


```{r filter-section1-read data}
data <- read.csv('daily-caloric-supply-derived-from-carbohydrates-protein-and-fat.csv')

mydata <- data %>% filter(Entity %in% c("United States","Japan"))
```

```{r missing_section_data, eval=FALSE}
pct_miss(mydata) #0 missingness in the UK and Iceland data
pct_miss_case(mydata)
pct_miss_var(mydata)
```


```{r data preprocessing}

mydata <- mydata %>% 
  mutate(total_Cal = Calories.from.animal.protein..FAO..2017..
         +Calories.from.plant.protein..FAO..2017..
         +Calories.from.fat..FAO..2017..
         +Calories.from.carbohydrates..FAO..2017..,
         Protein_Cal=Calories.from.animal.protein..FAO..2017..
         +Calories.from.plant.protein..FAO..2017..,
         `Protein(%)`=percent((
           Calories.from.animal.protein..FAO..2017..
           +Calories.from.plant.protein..FAO..2017..)/total_Cal,
           accuracy = 4),
         `Fat(%)`=percent(
           Calories.from.fat..FAO..2017../total_Cal
           ,accuracy = 4),
         `Carbohydrates(%)`=percent(
           Calories.from.carbohydrates..FAO..2017../total_Cal,
           accuracy = 4))%>%
  rename(Fat_Cal=Calories.from.fat..FAO..2017..,
         Carbohydrates_Cal=Calories.from.carbohydrates..FAO..2017..,
         Animal_Protein_Cal=Calories.from.animal.protein..FAO..2017..,
         Plant_Protein_Cal=Calories.from.plant.protein..FAO..2017..)
mydata=mydata%>%
  filter(Year<=2010)%>%
  filter(Year>=1961)

US_Data <- mydata %>% filter(Entity =="United States") 

Japan_Data <- mydata %>% filter(Entity =="Japan")

mydata <- US_Data %>% rbind(Japan_Data)

mydata_long <- mydata %>% 
  pivot_longer(cols=c(total_Cal,Protein_Cal, Fat_Cal,Carbohydrates_Cal ),
               names_to = "impact_variable", values_to = "measure")
```


\addcontentsline{toc}{subsection}{Question1}
\subsection*{Question1}
(1)What is the difference in the proportions of total Calories and the three major nutrients (protein, fat, carbohydrate) from 1970 in the American and Japanese diets?

```{r ThreemajorComparision, tab.cap = "Energy Consumption Comparision"}
mydata %>% 
  pivot_wider(id_cols = c(Year),
              names_from = Entity,
              values_from = c(total_Cal)) %>%
  filter(Year>=1970)%>%
  arrange(desc(Year)) %>%
  knitr::kable(caption = "Proportions of the Nutrients Comparision")
```


```{r proportion_countries_yearly, fig.cap="Proportion Share Across The Years", include=FALSE}
mydata_long %>% ggplot() +
  geom_col(mapping = aes(x = Year, y = measure, fill = Entity), position="fill")+facet_wrap(~impact_variable, nrow = 2)+ylab("Proportion")
```
\begin{figure}[H]
\includegraphics[width=6in, height = 2in]{Figures/proportion_countries_yearly-1}
\caption{Proportion Share Across The Years}
\label{fig:proportion_countries_yearly}
\end{figure}

Figure 1 and Table 1 show that from 1961 to 2010, the share of per capita calorie intake in the United States and Japan did not change much, with the United States consistently having slightly higher calorie intake than Japan.
From the perspective of the proportion of the three major nutrients of protein, fat and carbohydrates, the intake of fat in the American people's diet is much higher than that of the Japanese, and the intake of carbohydrates in the daily diet of the Japanese is higher than that of the United States. people. For protein intake, Americans and Japanese intakes are not much different.
In summary, we can find that in terms of dietary habits, Japan and the United States show significant differences in the ratio of carbohydrates and fats in calorie intake. The American diet has more calories from fat, while the Japanese diet has more carbohydrates.
